Genome-wide changes in expression during inflorescence architecture development

### 2015-08-13 ms.Rmd
rtracklayer needed update???

+ Max. 1 paragraph about boring sequencing stats
+ **Table** (or supplementary): # reads, mapping %, rRNA, introns, genes blah blah

@@

>>>>

+ Max. 1 paragraph about boring sequencing stats
+ **Table** (or supplementary): # reads, mapping %, rRNA, introns, genes blah blah
+ Description of the dataset

@@

The presence of MADS genes was enriched in **which clusters** and their overall expression is enriched in the spikelet meristem sample. These results correspond with previous studies that have established the importance of MADS genes in inflorescence development. The evolution of their expression patterns was
